---
title: "Situation analysis"
---

## Market overview

Vietnam’s power tools market is growing steadily, driven by the country’s expanding construction, infrastructure, and manufacturing sectors. Segments such as HVAC, MEP, and civil works are becoming more professionalized, opening the door for advanced cordless technologies. Key highlights are presented as below:

-	The power tools market in Vietnam was valued at approximately USD 1.3 billion in 2023 (Ken Research).
-	The construction equipment segment reached 6.12 thousand units in 2023 and is projected to grow to 7.90 thousand units by 2029, with a CAGR of 4.35% (Arizton).
-	Vietnam’s broader construction market is expected to grow from USD 68.75 billion in 2024 to USD 110.42 billion by 2030, at a CAGR of 8.1% (Mordor Intelligence).
-	Demand for cordless power tools is gradually rising in urban areas due to increasing concerns over safety, mobility, and noise reduction, especially in HVAC and indoor applications.

*PESTEL Analysis:*

| **Factor**       | **Relevance to Milwaukee Vietnam**                                      |
|------------------|-------------------------------------------------------------------------|
| **Political**    | Regulations on tool safety, import tariffs, and workplace standards.    |
| **Economic**     | Fuel cost vs. electricity, rising input costs, price-sensitive purchasing. |
| **Social**       | Deep discounting mindset; legacy usage of gasoline/corded tools.        |
| **Technological**| Increased interest in lithium battery tools and smart diagnostics.      |
| **Legal**        | Safety compliance, warranty enforcement, and local standards.           |
| **Environmental**| Cordless tools offer cleaner, quieter operation; aligns with green trends. |

Milwaukee Vietnam at a glance:

-	Entered the Vietnamese market in 2019
-	Operates via 58 distributors and 124 sub-dealers nationwide.
-	Offers over 300 SKUs, primarily in cordless drills, wrenches, saws, and accessories.
-	Estimated annual revenue in Vietnam: 326 billion VND
-	Year-over-year revenue growth (2024 vs. 2023): 32%
-	Key focus segments: HVAC contractors, electricians, infrastructure teams.
-	Current market stage: early penetration, with limited top-of-mind awareness outside of trade circles.
Sao khong len ta

## Competitor snapshot

Test diagram


```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(ggimage)
library(moments)

cleanup <- theme(panel.grid.major = element_blank(),
                 panel.grid.minor = element_blank(),
                 panel.background = element_blank(),
                 axis.line.x = element_line(color = "black"),
                 axis.line.y = element_line(color = "black"),
                 legend.key = element_rect(fill ="white"),
                 text = element_text(family = "serif", size = 14),
                 plot.title = element_text(face = "bold", hjust = 0.5))

freq_percent <- function(x) {
  freq <- table(x)
  percentage <- prop.table(freq)*100
  percentage <- round(percentage, 2)
  result <- data.frame(
    value = names(freq),
    Frequency = as.vector(freq),
    Percentage = as.vector(percentage)
  )
  return(result)
}


# Data: put your logos in a folder (e.g., "images/")
brands <- data.frame(
  brand      = c("Milwaukee","DeWalt","Bosch","Makita"),
  price      = c(8.6, 7.8, 7, 6),
  durability = c(8.8, 7.2, 6, 6.2),
  logo       = c("image/milwaukeelg.png",
                 "image/dewaltlg.png",
                 "image/boschlg.png",
                 "image/makitalg.png"),
  size = c(50, 50, 50, 50)
)

ggplot(brands, aes(price, durability)) +
  geom_hline(yintercept = 6.6, color = "grey55", linewidth = 0.7) +
  geom_vline(xintercept = 6.5, color = "grey55", linewidth = 0.7) +
  geom_image(aes(image = logo), size = 0.18, asp = 1) +
  coord_cartesian(xlim = c(4,9), ylim = c(4.5,9), expand = FALSE) +
  labs(x = "Price (Low → High)", y = "Durability (Low → High)",
       title = "Market Positioning by Price and Durability") +
  cleanup + 
  theme(
    axis.text.x  = element_blank(),
    axis.text.y  = element_blank(),
    axis.ticks   = element_blank()
  )
```

Test pie chart

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)

# Data
budget <- data.frame(
  category = c(
    "Paid Media (FB, TikTok, YouTube)",
    "Influencer / KOL / KOC Activation",
    "On-ground Activation (RedTest)",
    "POS & Retail Support",
    "Content Production",
    "CRM / Zalo Engagement",
    "AI Integration / App One-Key",
    "Tracking, Reporting & Contingency"
  ),
  percent = c(32, 18, 16, 10, 9, 6, 5, 4)
)


# Pie chart
ggplot(budget, aes(x = "", y = percent, fill = category)) +
  geom_col(width = 1, color = "white") +
  coord_polar(theta = "y") +
  geom_text(aes(label = paste0(percent, "%")),
            position = position_stack(vjust = 0.5), size = 4, family = "serif") +
  labs(title = "Estimated Total Budget: $880K USD", x = NULL, y = NULL, fill = "Category") +
  cleanup

```